\section*{Acknowledgments}

It is not possible to arrive at this stage -- finishing a PhD project -- without the help and influence
of a considerable amount of people and chances are high that I will have forgotten to mention some of them.
This section will present my gratitude towards all the countless people who have been important to me
on my way to where I am now in a perceived chronological order.

\vspace{1em}
\noindent Firstly I have to thank my fellow undergraduate students, especially \emph{Peter Freiwang},
\emph{Daniel Reiser} and \emph{Alexis Kassiteridis} for treading the path with me
and for showing me what is important
-- albeit by giving a negative example in one particular case.
Another person who must be mentioned is Prof. Dr \emph{Harald Lesch} who not only awoke my interest in physics
when I was young but also turned out to be an inspiring professor, not only of Astrophysics but
especially in Philosophy.

\noindent Special thanks for arousing my interest in accelerator physics go to Prof. \emph{Lenny Rivkin} and
\emph{Adrian Oeftiger}.

\vspace{1em}
\noindent I would like to acknowledge the assistance I received from the following people:
My supervisors Prof. Dr \emph{Wolfgang Hillert} and Dr \emph{Rogelio Tom\'as} for their
knowledge, mentoring and guidance and for never discarding far fetched ideas,
my colleagues \emph{Ewen Maclean} and \emph{Tobias Persson} for many fruitful discussions
and answering countless questions, and to \emph{Andrea Franchi} for showing me the path into the realm of
RDTs and the normal form approach.
Additional thanks go to Prof. Dr \emph{Bernard Parisse} for acting as counterweight against the
many premature ideas that I and my colleagues have and for grounding my opinions
on our research methods.

\vspace{1em}
\noindent I want to thank my colleagues and friends here at CERN for the memorable time,
both in the office and in our free time, be it in person or virtual:
\emph{Marco D'Andrea},
\emph{Sondre Vik Furuseth},
\emph{Alexander Krainer},
\emph{Elena Fol},
\emph{Joschua Dilly},
\emph{Felix Carlier},
\emph{Leon van Riesen-Haupt}
and
\emph{Felix Soubelet}.

\noindent Some deserve a special mention:\\
\emph{Michael Hofer} for being at the same time an invaluably helpful and incredibly annoying
office mate, for his view of the bigger picture, his bad jokes and the tea and cookie times.\\
\emph{Jaime Coello de Portugal} (and I skip the rest of his name) for an enthusiastic
introduction to programming,
our discussions about computer games
and for pulling me into some fun hobby projects like soldering my own keyboard.\\
And \emph{Marian Lückhof} for the many, many discussions and for preferring early lunch.

\noindent And last but not least I want to express my deep gratitude towards my family: My parents, \emph{Martin}
and \emph{Sigrid} who raised me to become the person I am now, for believing in me and supporting me.
And of course to \emph{Lorène} for being in my life, the adventures we share and for supporting me during these long years of the PhD project.

\vspace{2em}
\noindent This work is sponsored by the Wolfgang Gentner Program of the German Federal Ministry
of Education and Research (05E15CHA).